---
title: "Using metaspace_Fetch"
author: "Jonathan A Ruepong"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
library(reticulate)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`metadata_fetch` is included in the metadata-workflow package. It provides a way to interact with METASPACE by searching, filtering, and downloading mass spectrometry imaging data. This uses the metaspace2020 api to connect to the server and provide other functionalities.

`metadata_fetch` has several key functions to use:

* The **search_metaspace()** function enables searching on the METASPACE server itself. Each parameter corresponds to a filter the metaspace2020 api enables to search with. This returns a list of objects (SMObjects) the metaspace2020 api uses. Each object corresponds to a dataset on METASPACE.

* The **make_dataframe()** function makes a dataframe out of a list of dataset objects. The dataframe includes information for each dataset included in the list you give.

* The **filter_metadata()** function can filter a dataframe of dataset objects. It will filter by the values or keys given to it as a list of arguments for a specific parameter. It will return a new dataframe after filtering.

* The **filter_molecule()** function can filter a dataframe based on molecules detected in a dataset. It works the same as the `filter_metadata()` function. Where you give a list of values to filter with as an argument.

* The **annotate()** function adds a new column to your dataframe. This new column is called "Molecules" which stores all annotation information on the molecules detected in that dataset.

* The **dataset_selection()** function is used to download selected datasets. Select a column to select the datasets by, and then give it a list of datasets or values to choose which datasets to download. It also can download all datasets from your dataframe.

## In-depth look on key functinons

`search_metaspace()` calls on the `datasets()` function used by the metaspace2020 api to search for datasets on METASPACE. Each parameter in the `search_metaspace()` function is a filter used to find datasets matching the criteria. The function returns a list of dataset objects (SMObjects) which the metaspace2020 api uses to represent datasets. Each parameter is optional as calling the function without any arguments returns all available datasets on METASPACE.

Parameters:

* **keyword** takes in a string. This searches by keyword on METASPACE. It finds matches based on a dataset's name.

* **datasetID** takes in a list. Given a list of dataset IDs, it will search METASPACE by ID.

* **submitter_ID** takes in a string. It searches METASPACE by submitter ID.

* **group_ID** takes in a string. It searches METASPACE by group ID.

* **project_ID** takes in a string. It searches METASPACE by project ID.

* **polarity** takes in a string(POSITIVE,NEGATIVE). It searches METASPACE by polarity.

* **ionisation_Source** takes in a string. It searches METASPACE by the ionisation source.

* **analyzer_Type** takes in a string. It searches METASPACE by the analyzer type.

* **maldi_Matrix** takes in a string. It searches METASPACE by maldi matrix.

* **organism** takes in a string. It searches METASPACE by organism.

`make_dataframe()` functions as a way to present more information of the datasets returned from `search_metaspace()`. The parameter `list_of_datasets` takes in a list of dataset objects. It will return a dataframe of thoses objects with more information on them.

Example dataframe:



Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
